%!TEX root = ../cv.tex
% -*- root: ../cv.tex -*-

%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publication}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
% Usage: \cvpublicationentry{<publisher>}{<title>}{<authors>}{<detail of publisher>}{<date>}{<description>}

\cvsubsection{International Journal}
\begin{cventries}

%---------------------------------------------------------
  \cvpublicationentry
    {Sensors} % Publisher
    {Fast Contour-Tracing Algorithm Based on a Pixel-Following Method for Image Sensors} % Title
    {\textbf{Jonghoon Seo}, Seungho Chae, Jinwook Shim, Dongchul Kim, Cheolho Cheong, and Tack-Don Han} % Authors
    {Vol. 16, Issue 3, pp. 353}
    {9, Mar. 2016} % Date(s)
    {http://dx.doi.org/10.3390/s16030353}

%---------------------------------------------------------
  \cvpublicationentry
    {Virtual Reality} % Publisher
    {Gesture-based interactive augmented reality content authoring system using HMD} % Title
    {Jinwook Shim, Yoonsik Yang, Nahyung Kang, \textbf{Jonghoon Seo}, and Tack-Don Han} % Authors
    {Vol. 20, Issue 1, pp. 57-69}
    {12, Jan. 2016} % Date(s)
    {http://dx.doi.org/10.1007/s10055-016-0282-z}

\end{cventries}

\cvsubsection{Domestic Journal}
\begin{cventries}

%---------------------------------------------------------
  \cvpublicationentry
    {J. of Korea Multimedia Society} % Publisher
    {Region-growing based Hand Segmentation Algorithm using Skin Color and Depth Information} % Title
    {\textbf{Jonghoon Seo}, Seungho Chae, Jinwook Shim, Hayoung Kim, and Tack-Don Han} % Authors
    {Vol. 16, Issue 9, pp. 1031-1043}
    {Sep. 2013} % Date(s)
    {http://www.dbpia.co.kr/Journal/ArticleDetail/NODE02277885}

  \cvpublicationentry
    {J. of Korea Multimedia Society} % Publisher
    {Augmented Reality Authoring Tool with Marker \& Gesture Interactive Features} % Title
    {Jinwook Shim, Minje Kong, Hayoung Kim, Seungho Chae, Kyungho Jung, \textbf{Jonghoon Seo}, Tack-Don Han} % Authors
    {Vol. 16, Issue 6, pp. 720-734}
    {Jun. 2013} % Date(s)
    {http://www.dbpia.co.kr/Journal/ArticleDetail/NODE02224153}

  \cvpublicationentry
    {J. of K-Assocaition of Inf. Edu.} % Publisher
    {Fundamental study on the technology and application for the Next Generation Digital Textbook} % Title
    {Won-Sung Sohn, Jae-Hyeop Han, Jin-Yong Choy, \textbf{Jonghoon Seo}, et al.} % Authors
    {Vol. 14, Issue 2, pp. 165-174}
    {Jun. 2010} % Date(s)
    {http://www.earticle.net/Article.aspx?sn=121727}


\end{cventries}

\cvsubsection{International Conference}
\begin{cventries}
%---------------------------------------------------------
  \cvpublicationentry
    {ICASSP} % Publisher
    {Realtime plane detection for projection Augmented Reality in an unknown environment} % Title
    {Dongchul Kim, Seungho Chae, \textbf{Jonghoon Seo}, Yoonsik Yang, Tack-Don Han} % Authors
    {Proceedings of IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP), 2017}
    {Mar. 2017} % Date(s)
    {https://doi.org/10.1109/ICASSP.2017.7953305}

%---------------------------------------------------------
  \cvpublicationentry
    {SMC} % Publisher
    {ColorCodeAR: Large identifiable ColorCode-based augmented reality system} % Title
    {Seungho Chae, \textbf{Jonghoon Seo}, Yoonsik Yang, and Tack-Don Han} % Authors
    {Proceedings of IEEE International Conference on Systems, Man, and Cybernetics 2016}
    {Oct. 2016} % Date(s)
    {https://doi.org/10.1109/SMC.2016.7844630}

%---------------------------------------------------------
  \cvpublicationentry
    {SA} % Publisher
    {LaserTouch: touch device control using a laser pointer} % Title
    {Seungho Chae, \textbf{Jonghoon Seo}, Yoonsik Yang, and Tack-Don Han} % Authors
    {SIGGRAPH Asia 2014 Posters, pp. 20:1}
    {Nov. 2014} % Date(s)
    {http://doi.acm.org/10.1145/2668975.2668982}

%---------------------------------------------------------
  \cvpublicationentry
    {KJMR} % Publisher
    {Real-time Tour Map Recognition and Tracking for Mobile Tour Guide Systems} % Title
    {Heeseung Choi, \textbf{Jonghoon Seo}, Seungho Chae, Yoonsik Yang, and Ig-Jae Kim} % Authors
    {Proceedings of the 7th Korea-Japan Workshop on Mixed Reality(KJMR) 2014}
    {Apr. 2014} % Date(s)
    {http://www.imrc.kist.re.kr/wiki/KJMR2014}

%---------------------------------------------------------
  \cvpublicationentry
    {IUI} % Publisher
    {AR Lamp: interactions on projection-based augmented reality for interactive learning} % Title
    {Jeongyun Kim, \textbf{Jonghoon Seo}, and Tack-Don Han} % Authors
    {Proceedings of the 19th International Conference on Intelligent User Interfaces(IUI), pp. 353-358}
    {Feb. 2014} % Date(s)
    {http://dx.doi.org/10.1145/2557500.2557505}

%---------------------------------------------------------
  \cvpublicationentry
    {ICCE} % Publisher
    {Interactive features based augmented reality authoring tool} % Title
    {Jinwook Shim, Minje Kong, Yoonsik Yang, \textbf{Jonghoon Seo}, and Tack-Don Han} % Authors
    {Proceedings of the 2014 IEEE International Conference on Consumer Electronics(ICCE), pp. 47-50}
    {2014} % Date(s)
    {http://dx.doi.org/10.1109/ICCE.2014.6775902}

%---------------------------------------------------------
  \cvpublicationentry
    {CHI EA} % Publisher
    {AR pen and hand gestures: a new tool for pen drawings} % Title
    {Hark-Joon Kim, Hayoung Kim, Seungho Chae, \textbf{Jonghoon Seo}, and Tack-Don Han} % Authors
    {CHI '13 Extended Abstracts on Human Factors in Computing Systems, pp. 943-948}
    {Apr. 2013} % Date(s)
    {http://dx.doi.org/10.1145/2468356.2468525}

%---------------------------------------------------------
% 5.  Hark-Joon Kim, Jonghoon Seo, Hayoung Kim, Seoungho Chae, Tack-Don Han, “AugGesture Pen: Using non-dominant hand gestures for augmenting pen-based tasks”, DIS(Designing Interactive Systems) 2012, 2012, (Link)
  \cvpublicationentry
    {DIS} % Publisher
    {AugGesture Pen: Using non-dominant hand gestures for augmenting pen-based tasks} % Title
    {Hark-Joon Kim, \textbf{Jonghoon Seo}, Hayoung Kim, Seoungho Chae, and Tack-Don Han} % Authors
    {DIS(Designing Interactive Systems) Poster in 2012}
    {Jun. 2012} % Date(s)
    {}

%---------------------------------------------------------
% 6.  Jonghoon Seo, Ji Hye Choi and Tack-don Han, “Image based Codes Performance Comparison for Mobile Environments”, Proceedings of the 14th International Conference on Human-Computer Interaction, Vol. 6761/2011, pp. 653-659, July 2011. (Link)
  \cvpublicationentry
    {HCII} % Publisher
    {Image based Codes Performance Comparison for Mobile Environments} % Title
    {\textbf{Jonghoon Seo}, Ji Hye Choi, and Tack-don Han} % Authors
    {Proceedings of the 14th International Conference on HCI International, Vol. 6761/2011, pp. 653-659}
    {Jul. 2011} % Date(s)
    {http://dx.doi.org/10.1007/978-3-642-21602-2_71}

%---------------------------------------------------------
% 7.  Jonghoon Seo, Jinwook Shim, Ji Hye Choi, James Park and Tack-don Han, “Enhancing Marker-based AR Technology”, Proceedings of the 14th International Conference on Human-Computer Interaction,  Vol. 6773/2011, pp. 97-104, July 2011. (Link)
  \cvpublicationentry
    {HCII} % Publisher
    {Enhancing Marker-based AR Technology} % Title
    {\textbf{Jonghoon Seo}, Jinwook Shim, Ji Hye Choi, James Park, and Tack-don Han} % Authors
    {Proceedings of the 14th International Conference on HCI International, Vol. 6773/2011, pp. 97-104}
    {Jul. 2011} % Date(s)
    {http://dx.doi.org/10.1007/978-3-642-22021-0_12}

%---------------------------------------------------------
% 8.  James Park, Jonghoon Seo, Ji-Hye Choi and Tack-Don Han, “ColoriT: Color Based Image Code Application to Aid in Memory Restoration of Offline Photo Artifacts”, Proceedings of the 14th International Conference on Human-Computer Interaction, Vol. 6761/2011, pp. 637-642, July 2011. (Link)
  \cvpublicationentry
    {HCII} % Publisher
    {ColoriT: Color Based Image Code Application to Aid in Memory Restoration of Offline Photo Artifacts} % Title
    {James Park, \textbf{Jonghoon Seo}, Ji-Hye Choi, and Tack-Don Han} % Authors
    {Proceedings of the 14th International Conference on HCI International, Vol. 6761/2011, pp. 637-642}
    {Jul. 2011} % Date(s)
    {http://dx.doi.org/10.1007/978-3-642-21602-2_69}

%---------------------------------------------------------
% 9.    Jinwook Shim, Jonghoon Seo and Tack-Don Han, “MSL_AR toolkit: AR Authoring tool with Interactive features”, Proceedings of the 14th International Conference on Human-Computer Interaction, Vol. 6773/2011, pp. 105-112, July 2011. (Link)
  \cvpublicationentry
    {HCII} % Publisher
    {MSL\_AR toolkit: AR Authoring tool with Interactive features} % Title
    {Jinwook Shim, \textbf{Jonghoon Seo}, and Tack-Don Han} % Authors
    {Proceedings of the 14th International Conference on HCI International, Vol. 6773/2011, pp. 105-112}
    {Jul. 2011} % Date(s)
    {http://dx.doi.org/10.1007/978-3-642-22021-0_13}

%---------------------------------------------------------
% 10.   Sung-Wook Baek, Jong-Hoon Seo and Tack-Don Han, “Meet Researcher in the Real World Using the ConAR: Context-Aware Researcher”, Proceedings of the 14th International Conference on Human-Computer Interaction, Vol. 6778/2011, pp. 12-19, July 2011. (Link)
  \cvpublicationentry
    {HCII} % Publisher
    {Meet Researcher in the Real World Using the ConAR: Context-Aware Researcher} % Title
    {Sung-Wook Baek, \textbf{Jong-Hoon Seo}, and Tack-Don Han} % Authors
    {Proceedings of the 14th International Conference on HCI International, Vol. 6778/2011, pp. 12-19}
    {Jul. 2011} % Date(s)
    {http://dx.doi.org/10.1007/978-3-642-21796-8_2}

%---------------------------------------------------------
% 11.   SungYoung Yoon, Jonghoon Seo, Junyoung Yoon, Seungchul Shin, and and Tack-Don Han, "A Usability Evaluation of Public Icon Interface", Lecture Notes in Computer Science (Proceedings of the 13th International Conference on Human-Computer Interaction), 2009, Vol. 5610/2009, pp. 540-546, July 2009. (Link)
  \cvpublicationentry
    {HCII} % Publisher
    {A Usability Evaluation of Public Icon Interface} % Title
    {SungYoung Yoon, \textbf{Jonghoon Seo}, Junyoung Yoon, Seungchul Shin, and Tack-Don Han} % Authors
    {Proceedings of the 13th International Conference on HCI International, Vol. 5610/2009, pp. 540-546}
    {Jul. 2009} % Date(s)
    {http://dx.doi.org/10.1007/978-3-642-02574-7_61}    % Link


%---------------------------------------------------------
% 12.   SeIn Lee, Jonghoon Seo, Soon-bum Lim, Yoon-Chul Choy, and and Tack-Don Han, "A Real-Time Hand Interaction System for image sensor based interface", Lecture Notes in Computer Science (Proceedings of the 13th International Conference on Human-Computer Interaction), 2009, Vol. 5611/2009, pp. 208-215, July 2009. (Link)
  \cvpublicationentry
    {HCII} % Publisher
    {A Real-Time Hand Interaction System for image sensor based interface} % Title
    {SeIn Lee, \textbf{Jonghoon Seo}, Soon-bum Lim, Yoon-Chul Choy, and Tack-Don Han} % Authors
    {Proceedings of the 13th International Conference on HCI International, Vol. 5611/2009, pp. 208-215}
    {Jul. 2009} % Date(s)
    {http://dx.doi.org/10.1007/978-3-642-02577-8_23}    % Link

%---------------------------------------------------------
% 13.   Dong-Chul Kim, Jong-Hoon Seo, Cheolho Cheong, Tack-Don Han, "Tag Interface for Pervasive Computing," Signal Processing and Multimedia, pp. 356-359, 2006.
  \cvpublicationentry
    {SIGMAP} % Publisher
    {Tag Interface for Pervasive Computing} % Title
    {Dong-Chul Kim, \textbf{Jong-Hoon Seo}, Cheolho Cheong, and Tack-Don Han} % Authors
    {Proceedings of the International Conference on Signal Processing and Multimedia Applications, pp. 356-359}
    {Aug. 2006} % Date(s)
    {}
%---------------------------------------------------------
\end{cventries}

\cvsubsection{Patents}
% Usage: \cvpatententry{<title>}{<authors>}{<patent no.>}{<date>}{<link>}

\begin{cventries}
  \cvpatententry
    {Mobile Terminal And Method For Controlling The Same} % Title
    {Suhwang Kim, \textbf{Jonghoon Seo}, Soonwon Hong, Hongbin Yang, Jeonghun Jang} % Authors
    {(submitted)US,20170150227A1} % patent no.
    {2016.09.19} % Date(s)
    {http://goo.gl/w6w41R}

  \cvpatententry
  % 국내특허, 등록번호 10-1632380, 서종훈, 한탁돈, 김동철, 신해준, 윤형민, 최창규, “바코드 인식 장치 및 방법”, 2016.06.15(등록) / 2009.10.19(출원)
    {Apparatus and Method for Recognizing Barcode} % Title
    {\textbf{Jonghoon Seo}, Tack-Don Han, Dongchul Kim, Haejun Shin, Hyongmin Yoon, Changkyu Choi} % Authors
    {KR, 10-1632380} % patent no.
    {2016.06.15} % Date(s)
    {http://goo.gl/blEyD8}

  \cvpatententry
  % 국내특허, 등록번호 10-1629737, 한탁돈, 서종훈, 채승호, 강나형, 김동철, “문자 입력 장치, 문자 입력 방법, 문자 입력을 위한 컴퓨터 판독가능 기록매체 및 컴퓨터 프로그램”, 2016.06.07(등록) / 2015.02.25(출원)
    {Method, Device, Computer Readable Recording Medium and Computer Program for Inputting Letters} % Title
    {Tack-Don Han, \textbf{Jonghoon Seo}, Seungho Chae, Nahyung Kang, Dongchul Kim} % Authors
    {KR, 10-1629737} % Publisher
    {2016.06.07} % Date(s)
    {http://goo.gl/5mRFtE}

  \cvpatententry
  % 국내특허, 등록번호 10-1586034, 한탁돈, 윤준영, 신해준, 김동철, 서종훈, 박선화, 윤형민, 최창규, “퍼셉티브 디스플레이 장치와 휴대용 단말기 간의 상호작용을 위한 장치 및 방법”, 2016.01.11(등록) / 2009.09.08(출원)
    {Apparatus and Method for Interaction Between Perceptive Display Unit and Portable Terminal} % Title
    {Tack-Don Han, Joonyoung Yoon, Haejun Shin, Dongchul Kim, \textbf{Jonghoon Seo}, et al.} % Authors
    {KR, 10-1586034} % Publisher
    {2016.01.11} % Date(s)
    {http://goo.gl/YRL6X2}

  \cvpatententry
  % 국내특허, 등록번호 10-1496761, 한탁돈, 서종훈, 심진욱, 박제희, 채승호, 김동철, “다면 스크린 프로젝션 기반 휴대용 3차원 모델 제어 시스템 및 그 방법”, 2015.02.23(등록) / 2014.08.25(출원)
    {3D Model Control System and Method Based on Multi-Screen Projection} % Title
    {Tack-Don Han, \textbf{Jonghoon Seo}, Jinwook Shim, James Park, Seungho Chae, Dongchul Kim} % Authors
    {KR, 10-1496761} % Publisher
    {2015.02.23} % Date(s)
    {http://goo.gl/J7NUdt}

  \cvpatententry
  % 국내특허, 등록번호 10-1483054, 한탁돈, 심진욱, 양윤식, 서종훈, 김동철, 박제희, “상호작용을 지원하는 모바일 기반 증강현실 제작 시스템 및 그 방법”, 2015.01.09(등록) / 2014.05.31(출원)
    {Mobile-based Augmented Reality Authoring System and Method for Interaction} % Title
    {Tack-Don Han, Jinwook Shim, Yoonsik Yang, \textbf{Jonghoon Seo}, Dongchul Kim, James Park} % Authors
    {KR, 10-1483054} % Publisher
    {2015.01.09} % Date(s)
    {http://goo.gl/uetUuh}

  \cvpatententry
  % 국내특허, 등록번호 10-1148027, 한탁돈, 박제희, 서종훈, 김동철, 최지혜, “멀티터치 센싱장치와 시스템 및 이를 위한 멀티터치 센싱방법”, 2012.05.15(등록) / 2011.01.25(출원)
    {Multi Touch Sensing Apparatus and System and Multi Touch Sensing Method for the Same} % Title
    {Tack-Don Han, James Park, \textbf{Jonghoon Seo}, Dongchul Kim, Asella Choi} % Authors
    {KR, 10-1148027} % Publisher
    {2012.05.15} % Date(s)
    {http://goo.gl/0X1vAi}
\end{cventries}